Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-06 volunteer-clouds-ieee-ci-si.tex
New data
Some fixes to earlier writing
There's still some pending work by @mariosky and @fergunet and reviewing answers to their comments.

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

@@

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Evolutionary algorithm, distributed computing, internet computing,
social networks, volunteer computing, metacomputing. 
\end{IEEEkeywords}

@@

Other systems, like JET, proposed by Soares et
al. \cite{soares1998get}, also used Java. JET supports 
the execution of parallel applications over the Internet and features
a comprehensive statistics collection subsystem, allowing its use for science,
since it allows the collection of algorithm analytics by the
experiment designer, unlike the other systems mentioned
above. Proposals contemporary to Jet, such as SuperWeb
\cite{alexandrov1997superweb} are roughly a translation of classical
distribution techniques, with complicated architectures that include
brokers for resource discovery. It is focused, however, in solving the
issues involved in browser-based computing and also in making a system
that is able to work across different classes of computers, mentioning
SPARCstations and PCs with Windows-95. Interestingly enough, this
paper incorporates a discussion on the economic model, paving the way
for the for-profit distributed computing systems that later on
arose. On the other hand, the potential for volunteer computing using
browsers was realized 
later on \cite{sarmenta-bayanihan} as well as the potential for
mischief of users with code in their hands
\cite{sarmenta-sabotagetolerance}. However, these early efforts by
Sarmenta once again used Java and not JavaScript, making this effort
less universal.

@@

There have been relatively few efforts to analyze the
performance that can be obtained from these volunteer computing
experiments. 
There were some initial attempts to simply dodge the issue by making
the algorithm adaptive to the kind of resources allotted to it
\cite{milani2004online}, which is actually not such a big problem in
algorithms such as the EA that can easily be
parallelized via population splitting or farming out evaluations to all
the nodes available. Lately, several approaches have focused on the
fault-tolerance of volunteer algorithms
\cite{gonzalez2010characterizing} which can, of course, be studied in
a more general distributed computing context
\cite{nogueras2015studying} or including it in a more general study of the
performance of the EA itself
\cite{DBLP:journals/gpem/LaredoBGVAGF14}.

>>>>

@@

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic}

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Evolutionary algorithms, evolutionary computation, distributed computing, internet computing,
social networks, volunteer computing, metacomputing. 
\end{IEEEkeywords}

@@

Other systems, like JET, proposed by Soares et
al. \cite{soares1998get}, also used Java. JET supports 
the execution of parallel applications over the Internet and features
a comprehensive statistics collection subsystem, allowing its use for science,
since it allows the collection of algorithm analytics by the
experiment designer, unlike the other systems mentioned
above. Other proposals contemporary to Jet, such as SuperWeb
\cite{alexandrov1997superweb} are roughly a translation of classical
distribution techniques, with complicated architectures that include
brokers for resource discovery. It is focused, however, in solving the
issues involved in browser-based computing and also in making a system
that is able to work across different classes of computers, mentioning
SPARCstations and PCs with Windows-95. Interestingly enough, this
paper incorporates a discussion on the economic model, paving the way
for the for-profit distributed computing systems that later on
arose. On the other hand, the potential for volunteer computing using
browsers was realized 
later on \cite{sarmenta-bayanihan} as well as the potential for
mischief of users with code in their hands
\cite{sarmenta-sabotagetolerance}. However, these early efforts by
Sarmenta once again used Java and not JavaScript, making this effort
less widespread.

@@

There have been relatively few efforts to analyze the
performance that can be obtained from these volunteer computing
experiments. 
There were some initial attempts to avoid the differences in performance
that could be obtained from volunteers  by making
the algorithm adaptive to the kind of resources allotted to it
\cite{milani2004online}, which is actually not such a big problem in
algorithms such as the EA that can easily be
parallelized via population splitting or farming out evaluations to all
the nodes available. Lately, several approaches have focused on the
fault-tolerance of volunteer algorithms
\cite{gonzalez2010characterizing} which can, of course, be studied in
a more general distributed computing context
\cite{nogueras2015studying} or including it in a more general study of the
performance of the EA itself
\cite{DBLP:journals/gpem/LaredoBGVAGF14}.
